{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-31 main.tex
Merge and Edit

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Function Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is getting more attention as researchers from different fields collect more data from a continuous underlying process. This data still can be processed by classical statistical methods, but only FDA allows answering questions that are tied to the information given by the smoothness of the underlying continuous process. (cf. \cite{levitin_introduction_2007})\\
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view one or more of the variables or units of a given data set as a smooth curve or function and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of a continuous underlying process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).

@@

	\subsection{Detailed Draft}
	\begin{itemize}
		\item Motivate random functions from introduction and the general concept of random variables
		\item Formalize random function in this context as random variables realizing in a Hilbert space
		\item Introduce $\mathbf{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
		\item Specialize to Hilbert space being $\mathbf{L}^2[0,1]$ for this context
		\item Define mean and covariance function of a random function realizing in $\mathbf{L}^2[0,1]$
		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbf{L}^2[0,1]$
		\item Introduce b-spline and Fourier bases
		\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbf{L}^2[0,1]$
		\item Explain the concept of iid data in a functional setting
		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
		\item Explain approximations of functional observations using truncated basis representations
		\item Introduce linear operator $L_1$ and sufficient condition associated with it
		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
	\end{itemize}
\subsection{Kokoszka Reimherr (2017) p51-53}
There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to Kokoszka and Reimherr (2017): In functional regression, the aim is not only to compute an estimate of the function $\beta$ because this function needs also to have an useful interpretation. Without this useful interpretation, there can be no effective and feasible prediction of the scalar responses from new explanatory functions. Hereby applies, that intervals with larger values of $|\beta(s)|$ are contributing more to to the response than small values of  $|\beta(s)|$. The sign of $\beta(s)$ within the intervals of the value s show either negative or positive association of  $|\beta(s)|$ for this interval. To get an useful interpretation, the estimate $\beta$ cannot jump in a seemingly random fashion, because then an useful interpretation is not possible and predictions from this model tend to have large variances and center around the mean of the responses. (see ~\cite{kokoszka_introduction_2017})

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Considering the population model of scalar-on-function linear regression
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because there are infinitely many solutions for finding the minimizing argument for $\hat{\beta}$. Define 
    \begin{equation}
  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
   \end{equation}
    \begin{equation}
     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
  	\end{equation}
   	\begin{equation}
    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
   \end{equation}

  This results in practice in a large number of equations, which are difficult to solve. Even if solved, this results in a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does bot utilize the intuition of smooth functions. Another reason why estimation is not feasible using this approach is colinearity. Approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
    \end{equation}, it becomes obvious that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$, so there will be vectors $X_{i}$ thatare stronlgx correlated and thus lead to large variances and not feasible estimation.

>>>>

	\begin{itemize}
		\item Describe the idea of regressing a scalar on functional data
		\item Describing the difference to multiple linear regression intuitively
		\item Giving an intuitive example
	\end{itemize}	
	Functional Data Analysis (FDA) is a relatively new field {\color{red} (roots in the 1940s Grenander and Karhunen)} which is gaining more attention as researchers from different fields collect data that is functional in nature. This data can often be processed by classical statistical methods, but only FDA allows extracting information given by the smoothness of the underlying process (cf. \cite{levitin_introduction_2007}).
	 As \cite{kokoszka_introduction_2017} describe, FDA should be considered when one can view variables or units of a given data set as smooth curves or functions and the interest is in analyzing samples of curves (cf. \cite[S.~17]{kokoszka_introduction_2017}).\\
	 To motivate scalar-on-function regression, consider the case of a data set containing a scalar response and observations of an underlying continuous process. In economics, one application could be the regression of stock market correlations on the Global Crisis Index (GCI), where the regression allows to assess the relationship between the correlation and the GCI at every point within a window (cf. \cite{Das_2019}).\\
	 The focus of this paper is to introduce Functional Linear Regression (FLR) in a scalar-on-function setting. We will be using the standard FLR framework, which relates functional predictors to a scalar response as follows:  {\color{red} (I don't set up any interval for s here we might do later...)}
	 \begin{equation}
	 	Y_{i} = \beta_{0} + \int{X_{i}(s)\beta(s)ds} + \epsilon_{i},
	 	\qquad i = 1, ..., n
	 \end{equation}
	 where the $X_{i}$ are observations of a random function $X$, $Y_i$ are realizations of the response variable and $\beta(s)$ is the coefficient function. The distinct feature of this framework is that the regressor is a function, which necessitates a different approach to estimation. As in the well-known framework of scalar linear regression, this is motivated by an interest in $\beta(s)$ for prediction. For instance, fluctuation in $X$ at a point $s_0$ will not have any effect on $Y$ if $\beta(s_0)$ = 0. \\
	 Estimation of $\beta(s)$ is inherently an infinite dimensional problem. In Section 2, after introducing the necessary theoretical concepts, we describe three methods of estimating a scalar coefficient function using a concept called truncated basis expansion. The results of the Monte-Carlo simulation regarding these three different methods are reported in Section 3. Finally, in Section 4, we test the prediction of FLR in a real world setting. {\color{red} (We may put some simple descriptions of results about each of MC and Application)}

@@

	\subsection{Detailed Draft}
	\begin{itemize}
		\item Motivate random functions from introduction and the general concept of random variables
		\item Formalize random function in this context as random variables realizing in a Hilbert space
		\item Introduce $\mathbf{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
		\item Specialize to Hilbert space being $\mathbf{L}^2[0,1]$ for this context
		\item Define mean and covariance function of a random function realizing in $\mathbf{L}^2[0,1]$
		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbf{L}^2[0,1]$
		\item Introduce b-spline and Fourier bases
		\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbf{L}^2[0,1]$
		\item Explain the concept of iid data in a functional setting
		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
		\item Explain approximations of functional observations using truncated basis representations
		\item Introduce linear operator $L_1$ and sufficient condition associated with it
		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
	\end{itemize}
\subsection{Kokoszka Reimherr (2017) p51-53}
There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ because this function also needs to have a useful interpretation. Without it, there might be prediction of the scalar responses from new explanatory functions, but the increase in understanding of the underlying question will be minimal. Thereby, intervals with larger values of $|\beta(s)|$ will contribute more to the response than small values of  $|\beta(s)|$. The sign of $\beta(s)$ indicates either negative or positive influence of $X(s)$ for a specific value of s. To get a useful interpretation, the estimate $\beta$ should not jump in a seemingly random fashion, because a useful interpretation of this erratic behavior will often be impossible and predictions from these model tend to have larger variances and to center around the mean of the responses. (see ~\cite{kokoszka_introduction_2017})

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Assuming a data generating process of the form:
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects. Define therefore
    \begin{equation}
  	c_{X}(t,s) = E[X(t)X(s)],\: c_{XY}(t) = E[X(t)Y], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{XY}(t) = E[X(t)\int \beta(t)X(s) \,dt \ +\epsilon
   \end{equation}
    \begin{equation}
     c_{XY}(t) = \int \beta(s)\,dt \: E[X(s)X(t)| X] + E[\epsilon |X]
  	\end{equation}
   	\begin{equation}
    	c_{XY}(t) = \int c_{X}(t,s) \beta(s) \,ds 
   \end{equation}

   In practice, this results in a large and often difficult to solve system of equations. Even if solved, the result is often a noisy function $\beta(\dot{•})$ that is not useful for interpretation since it does not utilize the intuition of smooth functions. Another reason why estimation is not feasible using this approach is colinearity. \\

   If we approximate the scalar-on-functional regression as
  	\begin{equation}
     Y_i = \sum_{i = 1}^{n} \beta(t_{i})X_1(t_{i}) + \epsilon_{i}
    \end{equation}, it becomes clear that if $t_{i}$ is close to $t_{i'}$, $X_{i}(t_{i})$ is close to $X_{i}(t_{i'})$ there will be vectors $X_{i}$ that are highly correlated and thus lead to large variances.
